Large Language Models in Reinforcement Learning - A Comparison of Methods

### 2023-11-13 doc/paper.tex
Add appendix ref
Signed-off-by: Jonatan Hanssen <jonatan.hanssen@outlook.com>

For the implementation details of our PPO and the hyperparameters used, see the Appendix.

@@

For text generation, we have decided to utilize an LLM from the Llama open-source family of language models developed by Meta AI, first released in Febraury, 2023. Specifically, we chose Llama 2, which has been trained using 40\% more data than its predecessor Llama 1, and has double the context length\cite{llama}. In the experiments presented below, we use the smallest version of Llama 2, with 7 billion parameters, which we download to run locally and reduce the bottleneck effect and cost of having to call an API to a model hosted by someone else. The reason for not using any of the larger Llama 2 models is simply the hardware limitation we face, with the 7B model requiring 19GB of VRAM to be run.

@@

On our final environment, we can see (Table \ref{unlockpickupresponses}) beneficial responses similar to the ones given in DoorKey. Here, we also see some absurd responses, which show that the LLM has completely misunderstood the prompt and few-shot examples. These responses are not particularly common, but they do occur sometimes and reveal some of the problems with running a relatively small LLM locally, as opposed to a larger model such as GPT4. These problems have been attempted remedied through prompt engineering (see the Appendix).

@@

\section*{Appendix}

>>>>

For the hyperparameters used in our PPO implementation, see the \nameref{sec:appendixtext}.

@@

For text generation, we have decided to utilize an LLM from the Llama open-source family of language models developed by Meta AI, first released in Febraury, 2023. Specifically, we choose Llama 2, which has been trained using 40\% more data than its predecessor Llama 1, and has double the context length\cite{llama}. In the experiments presented below, we use the smallest version of Llama 2, with 7 billion parameters, which we download to run locally and reduce the bottleneck effect and cost of having to call an API to a model hosted by someone else. The reason for not using any of the larger Llama 2 models is simply the hardware limitation we face, with the 7B model requiring 19GB of VRAM to be run.

@@

On our final environment, we can see (Table \ref{unlockpickupresponses}) beneficial responses similar to the ones given in DoorKey. Here, we also see some absurd responses, which show that the LLM has completely misunderstood the prompt and few-shot examples. These responses are not particularly common, but they do occur sometimes and reveal some of the problems with running a relatively small LLM locally, as opposed to a larger model such as GPT4. These problems have been attempted remedied through prompt engineering (see the \nameref{sec:appendixtext}).

@@

\section*{Appendix}
\label{sec:appendixtext}
